Uniform sampling across the whole territory without any cells

### 2024-09-05 First_steps/No_tree_no_grid.Rmd
Cleaner table

---
title: "Uniform sampling across the whole territory without any cells"
output: pdf_document
date: "2024-06-25"
---

@@

  # 3rd step: List of estimated totals thus obtained from each sample
  est_MC <- c()
  for (c in 1:B) {
    est_MC <- append(est_MC, sum((rho_MC[c])/p))
  }

  return(c(mean(est_MC), var(est_MC)))
  # Estimated value and Monte-Carlo variance
}
```

@@

# Table for comparison
diff_var <- data.frame(`Difference between totals` = paste0(round(mapply(function(x,y){unlist(100*(y-x)/x)}, unlist(THEO_df[1]), unlist(RES_df[1])), digits = 3), "%"), `Difference between variances` = paste0(round(mapply(function(x,y){unlist(100*(y-x)/x)}, unlist(THEO_df[2]), unlist(RES_df[2])), digits = 3), "%") )
# diff_var <- ifelse(diff_var == "NaN%", 0, diff_var)
diff_var[diff_var == "NaN%"] <- "0%"
```

```{r}
tab_var <- diff_var %>%
  kable("latex", booktabs = FALSE, align = "cc", linesep = c("", "", "",
  "\\addlinespace"), caption = paste("Assessment of the efficiency with samples with size 1000 and 1000 Monte Carlo iterations"), col.names = gsub("[.]", " ", names(diff_var))) %>%
  kable_styling(latex_options = "hold_position") %>%
  row_spec(0, bold = TRUE) %>% # , hline_after = TRUE
  collapse_rows(columns = 1, latex_hline = "major")
```

>>>>

---
title: "Uniform sampling across the whole territory without any cells"
output:
  html_document:
    df_print: paged
date: "2024-06-25"
---

@@

  # 3rd step: List of estimated totals thus obtained from each sample
  est_MC <- c()
  var_est <- c()
  for (c in 1:B) {
    est_MC <- append(est_MC, sum((rho_MC[c])/p))
    in_sum <- unlist(mapply(function(x){((x*area) - sum((rho_MC[c])/p))^2}, rho_MC[c]))
    var_est <- append(var_est, (1/(n*(n-1)))*sum(in_sum))
  }

  # var_est <- (1/(n(n-1)))*sum(in_sum)

  return(c(mean(est_MC), mean(var_est))) # , var(est_MC)
  # Estimated value and Monte-Carlo variance
}
```

@@

# Table for comparison
diff_var <- data.frame(Functions = c("$(x_1,x_2) \\mapsto 1$", "$(x_1,x_2) \\mapsto \\mathds{1} \\{x_1>x_2\\}$", "$(x_1,x_2) \\mapsto x_1$"), `Difference between totals` = paste0(round(mapply(function(x,y){unlist(100*(y-x)/x)}, unlist(THEO_df[1]), unlist(RES_df[1])), digits = 2), "\\%"), `Difference between variances` = paste0(round(mapply(function(x,y){unlist(100*(y-x)/x)}, unlist(THEO_df[2]), unlist(RES_df[2])), digits = 2), "\\%") )
diff_var[diff_var == "NaN\\%"] <- "0\\%" # In case unlist(THEO_df[X]) == 0
```

```{r MC_simple}
tab_var <- diff_var %>%
  kable("latex", escape = FALSE, booktabs = FALSE, align = "cc", linesep = c("", "", "",
  "\\addlinespace"), caption = paste("Assessment of the efficiency with samples with size 1000 and 1000 Monte Carlo iterations"), col.names = gsub("[.]", " ", names(diff_var))) %>%
  kable_styling(latex_options = "hold_position") %>%
  row_spec(0, bold = TRUE) %>% # , hline_after = TRUE
  collapse_rows(columns = 1, latex_hline = "major")
```
